### 2025-04-19 evaluating-prediction-accuracy.qmd
20250419 - calibration plot tweaks

plotRangeMax <- max(c(
  projectionsWithActuals_seasonal$raw_points,
  projectionsWithActuals_seasonal$fantasyPoints), na.rm = TRUE) + 50

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(0, plotRangeMax),
    expand = FALSE) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

@@

plotRangeMax <- max(c(
  projectionsWithActuals_seasonal_qb$raw_points,
  projectionsWithActuals_seasonal_qb$fantasyPoints), na.rm = TRUE) + 50

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal_qb,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(0, plotRangeMax),
    expand = FALSE) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections of Quarterbacks"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

@@

plotRangeMax <- max(c(
  projectionsWithActuals_seasonal_rb$raw_points,
  projectionsWithActuals_seasonal_rb$fantasyPoints), na.rm = TRUE) + 0

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal_rb,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(0, plotRangeMax),
    expand = FALSE) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections of Running Backs"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

@@

plotRangeMax <- max(c(
  projectionsWithActuals_seasonal_wr$raw_points,
  projectionsWithActuals_seasonal_wr$fantasyPoints), na.rm = TRUE) + 40

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal_wr,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(0, plotRangeMax),
    expand = FALSE) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections of Wide Receivers"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

@@

plotRangeMax <- max(c(
  projectionsWithActuals_seasonal_te$raw_points,
  projectionsWithActuals_seasonal_te$fantasyPoints), na.rm = TRUE) + 0

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal_te,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(0, plotRangeMax),
    expand = FALSE) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections of Tight Ends"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

@@

plotRangeMax <- max(c(
  projectionsWithActuals_seasonal_k$raw_points,
  projectionsWithActuals_seasonal_k$fantasyPoints), na.rm = TRUE) + 100

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal_k,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(0, plotRangeMax),
    expand = FALSE) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections of Kickers"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

@@

plotRangeMax <- max(c(
  projectionsWithActuals_seasonal_dl$raw_points,
  projectionsWithActuals_seasonal_dl$fantasyPoints), na.rm = TRUE) + 0

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal_dl,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(0, plotRangeMax),
    expand = FALSE) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections of Defensive Linemen"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

@@

plotRangeMax <- max(c(
  projectionsWithActuals_seasonal_lb$raw_points,
  projectionsWithActuals_seasonal_lb$fantasyPoints), na.rm = TRUE) + 0

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal_lb,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(0, plotRangeMax),
    expand = FALSE) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections of Linebackers"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

@@

plotRangeMax <- max(c(
  projectionsWithActuals_seasonal_db$raw_points,
  projectionsWithActuals_seasonal_db$fantasyPoints), na.rm = TRUE) + 0

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal_db,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(0, plotRangeMax),
    expand = FALSE) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections of Defensive Backs"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

>>>>

plotRangeMin <- min(calibrationLoessModel$lower, na.rm = TRUE)

plotRangeMax <- max(calibrationLoessModel$upper, na.rm = TRUE)

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(plotRangeMin, plotRangeMax),
    expand = FALSE) +
  scale_x_continuous(breaks = seq(0, plotRangeMax, by = 100)) +
  scale_y_continuous(breaks = seq(0, plotRangeMax, by = 100)) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

@@

plotRangeMin <- min(calibrationLoessModel$lower, na.rm = TRUE)

plotRangeMax <- max(calibrationLoessModel$upper, na.rm = TRUE)

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal_qb,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(plotRangeMin, plotRangeMax),
    expand = FALSE) +
  scale_x_continuous(breaks = seq(0, plotRangeMax, by = 100)) +
  scale_y_continuous(breaks = seq(0, plotRangeMax, by = 100)) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections of Quarterbacks"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

@@

plotRangeMin <- min(calibrationLoessModel$lower, na.rm = TRUE)

plotRangeMax <- max(calibrationLoessModel$upper, na.rm = TRUE)

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal_rb,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(plotRangeMin, plotRangeMax),
    expand = FALSE) +
  scale_x_continuous(breaks = seq(0, plotRangeMax, by = 100)) +
  scale_y_continuous(breaks = seq(0, plotRangeMax, by = 100)) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections of Running Backs"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

@@

plotRangeMin <- min(calibrationLoessModel$lower, na.rm = TRUE)

plotRangeMax <- max(calibrationLoessModel$upper, na.rm = TRUE)

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal_wr,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(plotRangeMin, plotRangeMax),
    expand = FALSE) +
  scale_x_continuous(breaks = seq(0, plotRangeMax, by = 100)) +
  scale_y_continuous(breaks = seq(0, plotRangeMax, by = 100)) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections of Wide Receivers"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

@@

plotRangeMin <- min(calibrationLoessModel$lower, na.rm = TRUE)

plotRangeMax <- max(calibrationLoessModel$upper, na.rm = TRUE)

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal_te,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(plotRangeMin, plotRangeMax),
    expand = FALSE) +
  scale_x_continuous(breaks = seq(0, plotRangeMax, by = 50)) +
  scale_y_continuous(breaks = seq(0, plotRangeMax, by = 50)) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections of Tight Ends"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

@@

plotRangeMin <- min(calibrationLoessModel$lower, na.rm = TRUE)

plotRangeMax <- max(calibrationLoessModel$upper, na.rm = TRUE)

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal_k,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(plotRangeMin, plotRangeMax),
    expand = FALSE) +
  scale_x_continuous(breaks = seq(0, plotRangeMax, by = 50)) +
  scale_y_continuous(breaks = seq(0, plotRangeMax, by = 50)) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections of Kickers"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

@@

plotRangeMin <- min(calibrationLoessModel$lower, na.rm = TRUE)

plotRangeMax <- max(calibrationLoessModel$upper, na.rm = TRUE)

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal_dl,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(plotRangeMin, plotRangeMax),
    expand = FALSE) +
  scale_x_continuous(breaks = seq(0, plotRangeMax, by = 20)) +
  scale_y_continuous(breaks = seq(0, plotRangeMax, by = 20)) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections of Defensive Linemen"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

@@

plotRangeMin <- min(calibrationLoessModel$lower, na.rm = TRUE)

plotRangeMax <- max(calibrationLoessModel$upper, na.rm = TRUE)

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal_lb,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(plotRangeMin, plotRangeMax),
    expand = FALSE) +
  scale_x_continuous(breaks = seq(0, plotRangeMax, by = 20)) +
  scale_y_continuous(breaks = seq(0, plotRangeMax, by = 20)) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections of Linebackers"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

@@

plotRangeMin <- min(calibrationLoessModel$lower, na.rm = TRUE)

plotRangeMax <- max(calibrationLoessModel$upper, na.rm = TRUE)

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal_db,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(plotRangeMin, plotRangeMax),
    expand = FALSE) +
  scale_x_continuous(breaks = seq(0, plotRangeMax, by = 20)) +
  scale_y_continuous(breaks = seq(0, plotRangeMax, by = 20)) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections of Defensive Backs"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```
